Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-09-21 article-models-ttdp.tex
evaluation operator(?)
editing derived.tex

@@

>>>>

\begin{comment}
\subsubsection{Introducing the evaluation operator}
The operation $\ctxev{A}{P}{\blank}$ brings things in context $\ctxext{{\Gamma}{A}}{P}$ to
the context $\ctxext{{\Gamma}{\mprd{A}{P}}}{\ctxwk{\mprd{A}{P}}{A}}$.
\begin{align*}
& \inference
  { \jfam{{{\Gamma}{A}}{P}}{Q}
    }
  { \jfamdefn
      {{{\Gamma}{\mprd{A}{P}}}{\ctxwk{\mprd{A}{P}}{A}}}
      {\ctxev{A}{P}{Q}}
      {\subst{\evtm{A}{P}}{\ctxwk{\mprd{A}{P}}{Q}}}
    }
  \\
& \inference
  { \jfam{{{{\Gamma}{A}}{P}}{Q}}{R}
    }
  { \jfamdefn
      {{{{\Gamma}{\mprd{A}{P}}}{\ctxwk{\mprd{A}{P}}{A}}}{\ctxev{A}{P}{Q}}}
      {\ctxev[\famsym]{A}{P}{R}}
      {\subst{\evtm{A}{P}}{\ctxwk{\mprd{A}{P}}{R}}}
    }
  \\
& \inference
  { \jterm{{{{\Gamma}{A}}{P}}{Q}}{R}{h}
    }
  { \jtermdefn
      {{{{\Gamma}{\mprd{A}{P}}}{\ctxwk{\mprd{A}{P}}{A}}}{\ctxev{A}{P}{Q}}}
      {\ctxev[\famsym]{A}{P}{R}}
      {\ctxev[\tmsym]{A}{P}{h}}
      {\subst{\evtm{A}{P}}{\ctxwk{\mprd{A}{P}}{h}}}
    }
\end{align*}
\end{comment}

@@

\subsection{\texorpdfstring{$\Pi$}{Π}E-algebras}

\begin{defn}
An E-algebra $\cftalg{A}$ is said to be a $\Pi$E-algebra if there is 
an $E$-homomorphism
\begin{equation*}
\check\Pi:\cftfamalg{\cftfamalg{\cftalg{A}}}\to\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}
\end{equation*} 
in context $\ctxext{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}$, and a term
\begin{equation*}
\check{\mathsf{ev}}:
\end{equation*}
\end{defn}
